Trends of SDR in Thessaloniki

### 2023-06-25 DHI_GHI_2_sza_trends.tex
Commit 2023-06-26 01:17

\title{Trends of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-06-25}

@@

Time data span 1993-04-12, 2023-05-31

@@

\hypertarget{all-sky-cond.-dir.-beam-irrad.}{%
\paragraph{All sky cond. Dir. Beam Irrad.}\label{all-sky-cond.-dir.-beam-irrad.}}

@@

\hypertarget{clear-sky-cond.-dir.-beam-irrad.}{%
\paragraph{Clear sky cond. Dir. Beam Irrad.}\label{clear-sky-cond.-dir.-beam-irrad.}}

@@

\hypertarget{cloudy-cond.-dir.-beam-irrad.}{%
\paragraph{Cloudy cond. Dir. Beam Irrad.}\label{cloudy-cond.-dir.-beam-irrad.}}

@@

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrends-24} \end{center}

@@

\hypertarget{winter-all-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Winter All sky cond. Dir. Beam Irrad.}\label{winter-all-sky-cond.-dir.-beam-irrad.}}

@@

\hypertarget{winter-clear-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Winter Clear sky cond. Dir. Beam Irrad.}\label{winter-clear-sky-cond.-dir.-beam-irrad.}}

@@

\hypertarget{winter-cloudy-cond.-dir.-beam-irrad.}{%
\subsubsection{Winter Cloudy cond. Dir. Beam Irrad.}\label{winter-cloudy-cond.-dir.-beam-irrad.}}

@@

\hypertarget{spring-all-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Spring All sky cond. Dir. Beam Irrad.}\label{spring-all-sky-cond.-dir.-beam-irrad.}}

@@

\hypertarget{spring-clear-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Spring Clear sky cond. Dir. Beam Irrad.}\label{spring-clear-sky-cond.-dir.-beam-irrad.}}

@@

\hypertarget{spring-cloudy-cond.-dir.-beam-irrad.}{%
\subsubsection{Spring Cloudy cond. Dir. Beam Irrad.}\label{spring-cloudy-cond.-dir.-beam-irrad.}}

@@

\hypertarget{summer-all-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Summer All sky cond. Dir. Beam Irrad.}\label{summer-all-sky-cond.-dir.-beam-irrad.}}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-49} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-50} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-51} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-52} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-53} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-54} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-55} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-56} \end{center}

\hypertarget{summer-clear-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Summer Clear sky cond. Dir. Beam Irrad.}\label{summer-clear-sky-cond.-dir.-beam-irrad.}}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-57} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-58} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-59} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-60} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-61} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-62} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-63} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-64} \end{center}

\hypertarget{summer-cloudy-cond.-dir.-beam-irrad.}{%
\subsubsection{Summer Cloudy cond. Dir. Beam Irrad.}\label{summer-cloudy-cond.-dir.-beam-irrad.}}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-65} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-66} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-67} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-68} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-69} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-70} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-71} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-72} \end{center}

\hypertarget{autumn-all-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Autumn All sky cond. Dir. Beam Irrad.}\label{autumn-all-sky-cond.-dir.-beam-irrad.}}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-73} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-74} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-75} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-76} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-77} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-78} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-79} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-80} \end{center}

\hypertarget{autumn-clear-sky-cond.-dir.-beam-irrad.}{%
\subsubsection{Autumn Clear sky cond. Dir. Beam Irrad.}\label{autumn-clear-sky-cond.-dir.-beam-irrad.}}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-81} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-82} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-83} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-84} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-85} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-86} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-87} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-88} \end{center}

\hypertarget{autumn-cloudy-cond.-dir.-beam-irrad.}{%
\subsubsection{Autumn Cloudy cond. Dir. Beam Irrad.}\label{autumn-cloudy-cond.-dir.-beam-irrad.}}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-89} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-90} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-91} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-92} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-93} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-94} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-95} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_2_sza_trends_files/figure-latex/SzaTrendsSeas-96} \end{center}

@@

\begin{verbatim}
2023-06-25 17:38:40.8 athan@tyler DHI_GHI_1_longterm_trends.R 1.213719 mins
\end{verbatim}

>>>>

\title{Trends of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-06-26}

@@

Time data span 1993-04-12, 2011-03-31

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\begin{verbatim}
2023-06-25 21:52:15.8 athan@sagan DHI_GHI_1_longterm_trends.R 0.348333 mins
\end{verbatim}
